A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2018-11-28 manuscript/reply_to_reviewers.tex

		\textbf{R:}

	10. Explain Bayesian approach more simply [[done]]

		\begin{refquote}
		L147 Your Bayesian approach seems important, especially the prior information, and I would have appreciated it being explained more simply.
		\end{refquote}

		\textbf{R:} We have expanded our description of different types of priors and when researchers might prefer one over another. Following a comment from Reviewer 1 we have removed much of the mathematical background for the Bayesian approach, but this material is still present in the supplemental material. We hope that this simplifies the approach adequately.

@@

		\textbf{R:}

	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]

		\begin{refquote}
		L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.
		\end{refquote}

		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occurr at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study. We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}. Note that each posterior web is a prediction of the true metaweb and not a local realization of some interactions drawn from the feasible set. These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear. We have also added a line (lines XX-XX) to make this clear.
		\medskip
		This is an interesting point, however, as systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible. Assuming that all interactions which are known to be feasible actually occur at each site would also introduce bias - I suspect that this is what the Reviewer may be thinking of. As described above, our study cannot isolate $\chi$ (the probability that a feasible interaction occurs at a particular site), so this is not a relevant question for the present work. Future studies with much, much more detailed data may be able to shed light on this.

		\begin{quotation}
			we created a suite of 100 webs by randomly sampling from each posterior distribution. Each of these webs is a prediction of the structure of the metaweb.
		\end{quotation}

### 2018-11-28 manuscript/CI_interactions.tex
reply

  \subsection*{An empirical example}
    [[Make the point of this clearer]]
      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details). 
      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future. [[Needs a final line.]]

      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).

@@

      Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting. Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting, we created a suite of 100 webs by randomly sampling from each posterior distribution. After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.

>>>>

  \subsection*{An empirical example}
    [[Make the point of this clearer]]
      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details). 
      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We then calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda$).
      We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S5} for \emph{Salix}-galler results).

@@

      Using the prior distributions and procedures described above, we calculated posterior probability distributions for species pairs that were not observed interacting. Using these posterior distributions and assuming probabilities of 1 for pairs of species that were observed interacting (see \emph{Appendix S2} for a justification), we created a suite of 100 webs by randomly sampling from each posterior distribution. After obtaining these posterior networks, we calculated the connectance of each web, as well as the mean number of links per galler and per natural enemy, and the nestedness (NODF) of the network.

### 2018-11-28 manuscript/supplemental.tex
more revisions
reply

>>>>

    For interactions which were observed in at least one site ($k$\textgreater$0$), we can set the poseterior probability to 1 as long as the risk of a false positive is low. That is, when constructing a metaweb we can assume that an interaction observed at least once is truly feasible. The case study presented in the main text refers to a plant-galler network compiled by rearing galling insects obtained from galls; in each case, the plant-galler interaction definitely occurred and we are confident in the identification of both species involved (see \emph{Appendix S4} for details). Where the risk of false positives is higher (e.g., plant-pollinator networks where an observed flower visitor may not actually provide a pollination service), it may not be appropriate to assume $\lambda=$ wherever $k$\textgreater$0$. In such cases, we can model the posterior probabilities of observed interactions just as we do those that were not observed.

  \subsection*{Properties of the beta distribution}

    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

    %   The \textbf{average} of $\lambda$ is: 
    %       \begin{equation}
    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
    %         \label{mean}
    %       \end{equation}

    %     and its \textbf{variance} is:  
    %       \begin{equation}
    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
    %         \label{variance}
    %       \end{equation}

    %     The \textbf{mode} of the distribution is:
    %       \begin{equation}
    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
    %         \label{mode}
    %       \end{equation}
